\href{https://travis-ci.org/aracelis-git/Robot_Path_Planning}{\tt !\mbox{[}Build Status\mbox{]}(https\-://travis-\/ci.\-org/aracelis-\/git/\-Robot\-\_\-\-Path\-\_\-\-Planning.\-svg?branch=master)} 



\subsection*{Overview}

This R\-O\-S package provides a way for a robot to navigate a room by itself through self training. Using Q-\/learning, the robot navigates the room given a set reward and a learning rate constant.

\subsection*{S\-I\-P}

\href{https://drive.google.com/open?id=1vPMsvtIHx467KGZdfskSs1heT60qLzy87K0tlMnckY4}{\tt S\-I\-P Logs}

\href{https://drive.google.com/open?id=1AiFwYDx-4b8577_lUeq3aE7R47sUl6ZOjDB4g3GRvhU }{\tt Sprint Log }

\subsection*{License}

Copyright 2017 Aldrin I. Racelis

Licensed under the Apache License, Version 2.\-0 (the \char`\"{}\-License\char`\"{}); you may not use this file except in compliance with the License. You may obtain a copy of the License at

\href{http://www.apache.org/licenses/LICENSE-2.0}{\tt http\-://www.\-apache.\-org/licenses/\-L\-I\-C\-E\-N\-S\-E-\/2.\-0}

Unless required by applicable law or agreed to in writing, software distributed under the License is distributed on an \char`\"{}\-A\-S I\-S\char`\"{} B\-A\-S\-I\-S, W\-I\-T\-H\-O\-U\-T W\-A\-R\-R\-A\-N\-T\-I\-E\-S O\-R C\-O\-N\-D\-I\-T\-I\-O\-N\-S O\-F A\-N\-Y K\-I\-N\-D, either express or implied. See the License for the specific language governing permissions and limitations under the License.

\subsection*{Dependencies}

Turtlebot Gazebo Reinforcement Learning

This package has been tested with Ubuntu 14.\-04 and R\-O\-S Indigo.

\subsection*{Issues or Bugs}

Travis is not working correctly with the R\-O\-S testing.

\subsection*{Build}

After cloning the repository, do the following in the root directory\-:

catkin\-\_\-make roslaunch robot\-\_\-path\-\_\-planning robot\-\_\-path.\-launch

\subsection*{Tests}

Unit tests made with gtest verified the code. To run the test, execute the following code in the root directory.

catkin\-\_\-make run\-\_\-tests\-\_\-robot\-\_\-path\-\_\-planning

The unit tests are integrated with Travis, as seen by the badge at the top of the readme.

\subsection*{A\-P\-I}